The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum

### 2014-04-01 reviews/disc-ac1.tex
Add manuscript quotes (work in progress)
Add manuscript quotes (complete)

\renewcommand\thefigure{AC\arabic{figure}}
\def\referee#1{\bigskip\textcolor{journalname}{\textit{#1}}}

@@

These new figures present an altered version of climate forcing data used in our study, and they now more closely reflect how this data is read in by the ice sheet model, which seems appropriate for the discussion section. Moreover, the new maps reveal more clearly the strengths and weakness of different datasets, and support more strongly our interpretation of the ``hybrid'' climate forcing experiments presented in Sect.~5.2. These new figures are now included in the revised manuscript. Thank you very much for this constructive comment.

@@

A short discussion of these effects is given in Sect.~5.3, in the context of comparison of simulation results to the field evidence of the last glacial maximum ice margin. However you raise here a valid concern regarding potential ice sheet evolution to more similar states when accounting for precipitation changes, not considered in the current version of our manuscript. More particularly, in the east, where in most of our simulations, the ice margin does not attain a steady-state configuration, its position after 10\,kyr is largely determined by its rate of advance during the simulation length, which in turn depends on the amount of precipitation received. We agree that precipitation corrections in this region could slow down the ice margin advance, resulting in more similar configuration after 10\,kyr. We have included a discussion of this effect in Sect.~5.5.

>>>>

\renewcommand\thefigure{AC\arabic{figure}}
\def\referee#1{\bigskip\textcolor{journalname}{\textit{#1}}}
\def\msquote#1{\begin{quote}\textit{#1}\end{quote}}

@@

These new figures present an altered version of climate forcing data used in our study, and they now more closely reflect how this data is read in by the ice sheet model, which seems appropriate for the discussion section. Moreover, the new maps reveal more clearly the strengths and weakness of different datasets, and support more strongly our interpretation of the ``hybrid'' climate forcing experiments presented in Sect.~5.2. These new figures are now included in the revised manuscript, and caption and body text was reworked accordingly. Thank you very much for this constructive comment.

@@

However you raise here a valid concern regarding potential ice sheet evolution to more similar states when accounting for precipitation changes, not considered in the current version of our manuscript. More particularly, in the east, where in most of our simulations, the ice margin does not attain a steady-state configuration, its position after 10\,kyr is largely determined by its rate of advance during the simulation length, which in turn depends on the amount of precipitation received. We agree that precipitation corrections in this region could slow down the ice margin advance, resulting in more similar configuration after 10\,kyr. We have included a discussion of this effect in Sect.~5.5.

\msquote{As previously discussed, potential effects of the growing ice-sheet on precipitation changes are not included in our model. These changes likely consist of a reduction of precipitation in continental regions and in the ice sheet interior, and an increase of precipitation along part of the margin where the presence of ice imposed ascending winds, which could result in a thinner ice sheet than modelled here. In addition, the final position of the eastern ice margin is largely controlled by its advance rate through the run. Therefore, precipitation shadowing effects may have resulted in more similar ice-sheet configurations if they were included in the model. Although using a GCM of intermediate complexity may represent a first step towards including ice sheet feedback on climate, their spatial resolution does not allow for accurate resolution of orographic precipitation changes in a region as mountainous as the North American Cordillera.}

A more detailed discussion of potential effects of the growing ice-sheet on regional climate is given in Sect.~5.3 of the discussion paper, in the context of comparison of simulation results to the field evidence of the last glacial maximum ice margin.

### 2014-04-01 reviews/disc-ac2.tex
Add manuscript quotes (complete)

To clarify our methods, we have added the following paragraph:

@@

Although we do not believe that bedrock elevation must have been in equilibrium with the ice sheet configuration at the LGM, we recognize that through our simplistic palaeoclimatic approach, isostatic effects are another significant source of error on modelled ice surface elevation.

@@

In general, it became clear to us through your comments that we need more details about computation of bedrock deformation and its effects in the manuscript. These have been added in the revised version.

>>>>

To clarify our methods, we have reworked the last sentence of Sect.~2.1 into the following short paragraph:

@@

Although we do not believe that bedrock elevation must have been in equilibrium with the ice sheet configuration at the LGM, we recognize that through our simplistic palaeoclimatic approach, isostatic effects are another significant source of error on modelled ice surface elevation, as stated in a new paragraph of Sect.~5.5.

@@
